Verifying Demonstrations

### 2017-10-04 protocol.tex
Updates ProofFig, adds identifier construction to protocol

\begin{frame}
\begin{figure}
  \centering
  \mode<presentation>{%
    \only<1>{%
      \begin{tikzpicture}
        \tikzset{grow'=left,level distance=5em}
        \Tree [.proof
        {share}
        [.{share} {\(x,y\)} {$t_s'$} [.{\color{red}osig} {$t_s$} ]
        %[.tsig {$t_s''$} ]
        ]
        {share}
        ]
      \end{tikzpicture}
    }
  }
  \only<2>{%
    \begin{tikzpicture}
      \tikzset{grow'=left,level distance=5em}
      \Tree [.proof
      {share}
      [.{share} {\(x,y\)} {$t_s'$} [.{osig} 
      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s$} ]
      %[.tsig {$t_s''$} ]
      ]
      {share}
      ]
    \end{tikzpicture}
  }
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (share), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the \ac{tposet}.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnessed by a trusted witness (tsig).
    }%
    \label{ProofFig}
  }
\end{figure}

\mode<presentation>{%
  \only<1>{%
    \begin{idea}[Count once]
      \begin{itemize}
        \item Any two proofs by the same individual are linkable.
        \item Includes signature made by a verified key.
      \end{itemize}
    \end{idea}
  }

  \only<2>{%
    \begin{idea}[Designated event]
      \begin{itemize}
        \item Include a protest-specific identifier.
        \item E.g.\ hash of the \enquote{manifesto}.
      \end{itemize}
    \end{idea}
  }
}
\end{frame}

@@

We will start with the latter.
The identifier of the protest must be regulated, for the same reasons as for the 
user identifiers --- otherwise a counter-protest can simply choose the same 
protest identifier.
As was pointed out in \cref{CauseIsTheCommonDenominator}, the cause is at the 
root of what defines a protest.
The cause can be captured in some sort of \enquote{manifesto}, thus, we will use 
the hash value of the manifesto as identifier of the protest.
(As shown in \cref{ProofFig}.)

\Textcite{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another system that makes it non-interactive, see issue 
  \#27.
}.

>>>>

\begin{frame}
\begin{figure}
  \centering
  \begin{tikzpicture}
    \tikzset{grow'=left,level distance=5em}
    \Tree [.proof
    {share}
    [.{share} {\(wid\)} {\(l\)} {$t_s$} [.{\(pid\)} [.{\(cid\)} manifesto ] ]
    %[.tsig {$t_s''$} ]
    ]
    {share}
    ]
  \end{tikzpicture}
  \mode<article>{%
  \caption{%
    The proof depends on several proof shares.
    Each share depends on the protester's identifier (\(pid\), which depends on 
    the cause identifier, \(cid\)),
    the head of the blockchain (\(t_s\)), the location (\(l\)) and the witness 
    identifier (\(wid\)).
  }}%
  \label{ProofFig}
\end{figure}
\end{frame}

@@

We will start with the latter.
The identifier of the protest must be regulated, for the same reasons as for the 
user identifiers --- otherwise a counter-protest can simply choose the same 
protest identifier.
As was pointed out in \cref{CauseIsTheCommonDenominator}, the cause is at the 
root of what defines a protest.
The cause can be captured in some sort of \enquote{manifesto}, thus, we will use 
the hash value of the manifesto as identifier of the protest.
(As shown as manifesto and \(id\) in \cref{ProofFig}.)

\Textcite{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, e.g.\ by 
  \Textcite{Psignatures}, see issue \#27.
}.
Alice has a \ac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets PRF_k(id)\), which is her anonymous 
identity during the protest.
She must also provide \iac{NIZK} proof that \(pid = PRF_k(id)\) and that she 
knows a signature by the identity authority on \(k\).
Thus \(pid\) will be used as the unique identifier in the proof shares and the 
\ac{NIZK} proof will prove the eligibility of \(pid\).
